% 
% Annual Cognitive Science Conference
% Sample LaTeX Paper -- Proceedings Format
% 

% Original : Ashwin Ram (ashwin@cc.gatech.edu)       04/01/1994
% Modified : Johanna Moore (jmoore@cs.pitt.edu)      03/17/1995
% Modified : David Noelle (noelle@ucsd.edu)          03/15/1996
% Modified : Pat Langley (langley@cs.stanford.edu)   01/26/1997
% Latex2e corrections by Ramin Charles Nakisa        01/28/1997 
% Modified : Tina Eliassi-Rad (eliassi@cs.wisc.edu)  01/31/1998
% Modified : Trisha Yannuzzi (trisha@ircs.upenn.edu) 12/28/1999 (in process)
% Modified : Mary Ellen Foster (M.E.Foster@ed.ac.uk) 12/11/2000
% Modified : Ken Forbus                              01/23/2004
% Modified : Eli M. Silk (esilk@pitt.edu)            05/24/2005
% Modified : Niels Taatgen (taatgen@cmu.edu)         10/24/2006
% Modified : David Noelle (dnoelle@ucmerced.edu)     11/19/2014

%% Change "letterpaper" in the following line to "a4paper" if you must.

\documentclass[10pt,letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{color}
\definecolor{Green}{RGB}{10,200,100}
\newcommand{\ndg}[1]{\textcolor{Green}{[ndg: #1]}}





% check for obsolete LaTeX packages and outdated commands
% don't actually know what will happen
\RequirePackage[l2tabu, orthodox]{nag} 

% improve the spacing between words and letters
\usepackage{microtype} % used after fonts


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%% very basics %%%%%%%%%%%%%%%%

\usepackage{amsmath}
\usepackage{graphicx} % basic facilities
\usepackage{caption}

\usepackage{subfigure}  % should be updated!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%% special symbols %%%%%%%%%%%%%%%%

\usepackage{amssymb} % math symbols
\usepackage{stmaryrd} % logic

%\usepackage{tipa} % IPA symbols
%\usepackage{OTtablx} % OT Tableaux

%\usepackage{siunitx}  % 


%%%%%%%%%%%%%%%% reference-related packages %%%%%%%%%%%%%%%%

% create hyperlinks
\usepackage{hyperref} 
\hypersetup{colorlinks=true,citecolor=blue} % no ugly boxes

% apa-style citation
\usepackage{apacite} % has to be loaded after hyperref


% clever reference?? take some time to try this out
%\usepackage{cleveref}

%% if problems occur, consider comment out the above packages 

% ling examples

%\usepackage[equation]{gb4e-salt}
%\noautomath

\newcommand{\intp}[1]{\llbracket \text{#1} \rrbracket}

\title{A rational speech-act model of projective content}
%Conversational and conventional aspects of projective content: A rational speech-act model}

\author{{\large \bf Ciyang Qing}, {\large \bf Noah D.~Goodman}, {\large \bf Daniel Lassiter}\\
Stanford University} 

%\title{How to Make a Proceedings Paper Submission}
% 
%\author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\
%  Department of Psychology, 1202 W. Johnson Street \\
%  Madison, WI 53706 USA
%  \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\
%  Department of Educational Psychology, 1025 W. Johnson Street \\
%  Madison, WI 53706 USA}


\begin{document}



\maketitle
 
\begin{abstract}
Certain content of a linguistic construction can project when the construction is embedded in entailment-canceling environments.
 For example, the conclusion that John smoked in the past from the utterance \emph{John stopped smoking} 
 still holds for \emph{John didn't stop smoking}, in which the original utterance is 
 embedded under negation. 
 There are two main approaches to account for projection phenomena. 
 The semantic approach adds restrictions of the common ground to the conventional meaning.
 The pragmatic approach tries to derive projection from general conversational principles. 
 In this paper we build a probabilistic model of language understanding in which the listener 
  jointly infers the world state and what common ground the speaker has assumed. 
 We take change-of-state verbs as an example and model its projective content under negation. 
 Under certain assumptions, the model correctly predicts the projective behavior and its interaction with 
  the \emph{question under discussion} (QUD), without any special semantic treatment of projective content.

\textbf{Keywords:} 
Presupposition; projection; Bayesian pragmatics
\end{abstract}

\section{Introduction}
\label{sec:Intro}

\begin{quotation}
``When did you stop beating your wife?'' ---comedian
\end{quotation}

From \emph{John danced} we can infer \emph{John moved}, but we cannot infer this from \emph{John didn't dance}---the inference that \emph{John moved} is canceled by negation.
In contrast, from both \emph{John stopped smoking} and \emph{John didn't stop smoking} we are likely to infer that \emph{John used to smoke}---this inference is said to \emph{project} outside negation.
In natural language semantics and pragmatics, an inference that survives an operator that usually cancels inferences is called
 \emph{projective content} of the sentence under that operator. 
Change-of-state verbs can have information about the past as projective content under negation: \emph{John used to smoke} is projective content under negation of ``John stopped smoking.'' 
There are many other types of projective contents 
 (e.g., the complement of \emph{know}) under different operators 
 (e.g., questions, modals) identified and discussed in the literature. 
The problem of explaining how certain inferences can
 survive entailment-canceling operators is called the \emph{projection problem}.



%Natural language gives rise to various kinds of inferences. 
%One important class of such inferences is \emph{entailment}. 
%For example, from the sentence \emph{John danced} we can infer 
% that John moved. 
%When a sentence is embedded under certain operators, such as negation, 
% its entailments may no longer hold. 
%For the previous example, the negation of \emph{John danced}, i.e., 
% \emph{John did not dance}, no longer entails that John moved.
%This illustrates the well-known fact that negation is an
% \emph{entailment-canceling} operator.

%However, certain inferences seem to be able to survive entailment-canceling operators.
%For instance, think of a scenario in which Alice and Bob are talking about John, 
% an old friend of Alice's who is visiting her. 
%Bob has never met John before so he knows nothing about him. 
%Bob asks Alice, ``Does John smoke?'' 
%Alice replies, ``John stopped smoking.'' 
%At this point, what Bob infers about John from Alice's statement is twofold: 
% (i) that John does not smoke now, and (ii) that John smoked in the past.%
%\footnote{Alice's answer has another reading, which is about a particular smoking event 
% (e.g., John lit up a cigarette and finished it).
%We only discuss the habitual reading in this paper but our proposed analysis can be similarly 
% applied to the event reading.}
% 
%Both (i) and (ii) are highly plausible inferences and are arguably entailments of
% the sentence ``John stopped smoking.''
%But what happens when this sentence is embedded under negation? 
%That is, imagine another scenario which is identical to the previous one except that 
% Alice's reply is ``John did not stop smoking.'' 
%What would Bob infer in this case?
%Intuitively, it seems that Bob would infer (i$'$) that John smokes now, 
% and (ii$'$) that John smoked in the past.
% 
%Inferences (i) and (i$'$) are opposite.
%This is expected, since negation is an entailment-canceling operator.
%However, (ii) and (ii$'$) are exactly the same.
%This is surprising and puzzling: given that negation is entailment-canceling, 
% why and how does inference (ii) survive?
 

There are two main approaches to the projection problem.
According to the \emph{semantic} approach, projective contents are conventional properties of
 lexical items \cite<e.g.,>{frege1948sense,heimkratzer1998}. 
According to the \emph{pragmatic} approach, projection can be
 derived from general conversational principles 
 \cite<e.g.,>{Stalnaker1974:Pragmatic-Presuppositions,Simons2001:On-the-Conversational,simons2006foundational}. 
 How could we capture projection patterns using general conversational principles?
%``John did not stop smoking,'' is technically true even if John has never smoked. 
%Then how can Bob infer that John smoked in the past when Alice uses it in reply to his question whether John smokes?
%We will sketch the intuitive ideas here, and formalize them with a probabilistic model in the next section. 
To illustrate the reasoning, let us expand the example scenario:
Alice and Bob are talking about John, an old friend of Alice's who is visiting her. 
Bob has never met John before so he knows nothing about him. 
Bob asks Alice, ``Does John smoke?'' 
Alice replies, ``John did not stopped smoking.'' 
Taken literally, Alice's utterance seems under-informative: whether or not John smokes is compatible with what she said.
If Alice knows whether John smokes, is cooperative, and is able to directly address the question, she would not have said something under-informative.
So perhaps her answer is informative after all, but how?
Maybe she has taken some additional information for granted, assuming that it is in 
 the \emph{common ground} with Bob.
Indeed, if Alice took for granted that John smoked in the past, then, together with ``John did not stop smoking,'' this information would mean that John still smokes, which fully answers the question of whether John smokes now.
In other words, assuming that Alice took for granted that John smoked in the past best explains how Alice could be cooperative and still choose this utterance.
If Bob further assumes that if Alice took it for granted then it must be true, then he will arrive at the projected content: John used to smoke.
 
 
  There are many reasons why one might prefer such a pragmatic approach to projection to a 
 semantic one. 
First, change-of-state verbs systematically show projective behavior. 
Therefore, a generalization would be missing if their projective contents are
 lexically-encoded properties unrelated to each other.
Second, projection interacts with the contextual question under discussion,
 as can be seen from the following example \cite{Geurts1995:Presupposing}.
Imagine that Bob asked Alice: ``I notice that John keeps chewing on his pencil. Did he recently stop smoking?''
In this context Bob is interested in whether there was a change from smoking to non-smoking, rather than simply whether John is currently a smoker. 
As a result, he would not infer from an answer of ``no (it's just his habbit)'' that 
 John smoked in the past. 
Third, projection is sensitive to focus: ``John did not \emph{stop} smoking.'' seems to suggest he never smoked.
Yet a major obstacle to adopting the pragmatic approach has been the difficulty in formalizing the reasoning and showing that it emerges naturally from conversational principles.
 
In this paper, we build on and formalize previous ideas of the pragmatic approach.
We do so within the Rational Speech-Acts (RSA) framework  \cite{FrankGoodman2012:Predicting-Pragmatic-Reasoning-,GoodmanStuhlmuller2013:Knowledge-and-I}: a Bayesian 
approach to language understanding.
We extend the previous models by allowing the listener to reason about the facts that the speaker took to be in common ground (along similar lines to \cite{degen2015}).
We find that to account for the example scenario we must also make certain assumptions about which facts are plausible common ground and which question is under discussion.
With these assumptions and extensions, the model correctly accounts for projection phenomena of change-of-state verbs under negation.
It further predicts an interaction between projective behavior and the  
 \emph{question under discussion} (QUD) \cite{Roberts2012:Information-Structure}, suggesting an avenue for experimental research.

%The rest of the paper is as follows. We describe a sequence of extensions to the standard RSA model that ultimately predict the correct pattern of projection. 
%%pointing out each additional assumption needed and the motivation.
%Finally we discuss the full model's predictions, implications, and possible future directions.


\section{A Rational Speech-Act (RSA) model}
\label{sec:RSA}
\input{03_RSA}

\section{Question under discussion and projection}
\label{sec:Discussion}
\input{04_discussion}

\section{Conclusion and future direction}
\label{sec:Conclusion}
\input{05_conclusion}






\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\bibliography{presupposition,bgt_pragmatics}

\end{document}
